The globular cluster system of the Auriga simulations

### 2019-12-08 response_to_referee.tex

\documentclass{article}

\begin{document}

\section*{Introduction (of referee report)}
``The results of the paper clearly demonstrate that the technique of simulating
stellar clusters in cosmological hydrodynamical simulations by tagging stellar
particles based on their ages does not reproduce key properties of observed GC 
systems in the Milky Way and M31. However, the authors do not state this conclusion
anywhere''.

We feel that our conclusion would be too strongly phrased if we would generalise 
our results obtained using the Auriga simulations to cosmological simulations 
in general. Indeed, we do find that age-selected stellar particles do not 
reproduce key properties of observed GC systems in the Milky Way and M31. However,
our results might reflect characteristics that are specific to Auriga, 
e.g. that the galaxy formation model overmixes metals at early times. 
Therefore we did add a final bulletpoint to our conclusion to clarify the above, 
but we limit the scope to the Auriga simulations.

### 2019-12-08 AurigaGCS.tex
Response to Referee's conclusion that technique doesnt work for zoom-sims, but limit scope to Auriga

    \item The cluster formation efficiency would have to increase with decreasing
    metallicity for GC candidates in the Auriga simulations to be consistent
    with the MW GCS, given that we expect dynamical evolution to 
    more strongly affect GC candidates at smaller radii. This trend of over-production
    of old star particles that are metal-rich and at large radii compared to 
    observed GCs is less clear for the M31 GCS.

>>>>

    \item Tidal forces are larger in the inner regions of galaxies than in the
    outer halo. Therefore, we expect dynamical evolution to more strongly affect 
    GC candidates at small radii than at large radii. However,
    we find that the Auriga simulations produce more mass in GC candidates with
    high metallicities at large radii than with low metallicities at small radii.
    The cluster formation efficiency would have to increase with decreasing
    metallicity for GC candidates in the Auriga simulations to be consistent
    with the MW GCS. This trend of over-production of old star particles that 
    are metal-rich and at large radii compared to observed GCs is less clear for 
    the M31 GCS.

    \item
    Overall, we conclude that the metallicity and radial distribution of age-selected
    star particles in the Auriga simulations are not consistent with globular 
    cluster system of the Milky Way or with that of the Andromeda galaxy.
